A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2014-01-26 writeup/revision 1/paper.tex
Fixed typo
Cropped the quality bar graph to reduce whitespace

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=.9\linewidth]{figures/quality_bar.pdf}
\caption{Translation quality for languages with at least 50 Turkers. The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms. Error bars show the 95\% confidence intervals for each language.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\paragraph{Validation of controls} 
%Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google. We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
%
%As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.  We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz. }  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.  In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.  
%
%We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.53$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.    
%
%Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering
\footnotesize
\small
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
\footnotesize workers & \footnotesize  quality & \footnotesize speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}    Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low   &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&or medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low   &fast&--\\\cline{3-4}
&or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\normalsize
\caption{The green box shows the best languages to target on MTurk. These languages have many workers who generate high quality results quickly. We defined {\it many} workers as 50 or more active in-region workers, {\it high} quality as $\geq$70\% accuracy on the gold standard controls, and {\it fast} if all of the 10,000 words were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Discussion}
Crowdsourcing platforms like Mechanical Turk give researchers instant access to a diverse set of bilingual workers.  This opens up exciting new avenues for researchers to develop new multilingual systems.   The demographics reported in this study are likely to shift over time. Amazon may change its expand its payments to new currencies.  Posting long-running HITs in other languages may recruit more speakers of those languages.  New crowdsourcing platforms may emerge. The data presented here provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.

>>>>

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=.8\linewidth]{figures/quality_bar.pdf}
\caption{Translation quality for languages with at least 50 Turkers. The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms. Error bars show the 95\% confidence intervals for each language.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering
\footnotesize
%\small
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
\footnotesize workers & \footnotesize  quality & \footnotesize speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}    Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low   &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&or medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian,  Macedonian,  Malay,  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low   &fast&--\\\cline{3-4}
&or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\normalsize
\caption{The green box shows the best languages to target on MTurk. These languages have many workers who generate high quality results quickly. We defined {\it many} workers as 50 or more active in-region workers, {\it high} quality as $\geq$70\% accuracy on the gold standard controls, and {\it fast} if all of the 10,000 words were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
Crowdsourcing platforms like Mechanical Turk give researchers instant access to a diverse set of bilingual workers.  This opens up exciting new avenues for researchers to develop new multilingual systems.   The demographics reported in this study are likely to shift over time. Amazon may change its policies about who is eligible to participate or expand its payments to new currencies.  Posting long-running HITs in other languages may recruit more speakers of those languages.  New crowdsourcing platforms may emerge. The data presented here provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
